Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
clarify non-normality is not the focus of this paper

Residuals might also be plotted, as a scatter plot against the predicted values and each of the explanatory variables to scrutinize their relationships. If there is any visually discoverable patterns, the model is potentially misspecified. However, correctly judging a residual plot where no pattern exists is a painstakingly difficult task for humans. It is especially common, particularly among new data analytics students to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. However, for a consistent comparison, residual plot will be the focus of this paper. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the horizontal axis as shown in plot D of Figure \ref{fig:residual-plot-common-departures}.

>>>>

More typically, residuals will be plotted, as a scatter plot against the predicted values and each of the explanatory variables to scrutinize their relationships. If there is any visually discoverable patterns, the model is potentially misspecified. However, correctly judging a residual plot where no pattern exists is a painstakingly difficult task for humans. It is especially common, particularly among new data analytics students to report patterns when an experienced data analyst might quickly conclude that there are none. Generally, one looks for noticeable departures from the model like non-linear dependency or heteroskedasticity. It is also possible to conduct hypothesis tests for non-linear dependence [@ramsey_tests_1969], and use a Breusch-Pagan test [@breusch_simple_1979] for heteroskedasticity.

@@

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. For a consistent comparison, the residual plot of this departure is still presented in plot D of Figure \ref{fig:residual-plot-common-departures}. But since the scatter plot is not optimal for this task, non-normality will not be the focus of this paper. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the horizontal axis as shown in plot D of Figure \ref{fig:residual-plot-common-departures}.

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
clarify non-normality is not the focus of this paper

Residuals might also be plotted, as a scatter plot against the predicted
values and each of the explanatory variables to scrutinize their
relationships. If there is any visually discoverable patterns, the model
is potentially misspecified. However, correctly judging a residual plot
where no pattern exists is a painstakingly difficult task for humans. It
is especially common, particularly among new data analytics students to
report patterns when an experienced data analyst might quickly conclude
that there are none. Generally, one looks for noticeable departures from
the model like non-linear dependency or heteroskedasticity. It is also
possible to conduct hypothesis tests for non-linear dependence
\citep{ramsey_tests_1969}, and use a Breusch-Pagan test
\citep{breusch_simple_1979} for heteroskedasticity.

@@

\textbf{test}

>>>>

More typically, residuals will be plotted, as a scatter plot against the
predicted values and each of the explanatory variables to scrutinize
their relationships. If there is any visually discoverable patterns, the
model is potentially misspecified. However, correctly judging a residual
plot where no pattern exists is a painstakingly difficult task for
humans. It is especially common, particularly among new data analytics
students to report patterns when an experienced data analyst might
quickly conclude that there are none. Generally, one looks for
noticeable departures from the model like non-linear dependency or
heteroskedasticity. It is also possible to conduct hypothesis tests for
non-linear dependence \citep{ramsey_tests_1969}, and use a Breusch-Pagan
test \citep{breusch_simple_1979} for heteroskedasticity.

@@
